Centralizers of higher enveloping algebras of Lie algebras

### 2020-09-06 draft.tex
partway through section 4

Our approach here relies on a concrete and convenient model for these enveloping $E_n$ algebras by factorization algebras.
In particular, thanks to Knudsen \cite{Knudsen}, 
we know that the $E_n$ enveloping algebra $\UU_n \fg$ admits a model $\bU_n \fg$ whose underlying functor on the poset of open sets in $\RR^n$ assigns $\cliels(\Omega_c^*(V) \otimes \fg)$ to each open set~$V$.
There is another factorization algebra whose underlying assigns $\clies(\Omega^*(V) \otimes \fg)$ to each open~$V$.
Our paper shows that such factorization algebras model other important $E_n$ algebras, notably centralizers.

\begin{thm}
\label{thm: centralizer}
Let $\fg$ and $\fh$ be $L_\infty$ algebras over the real or complex numbers, 
and let $f: \fg \rightsquigarrow \fh$ be a homotopy-coherent morphism of $L_\infty$ algebras
(i.e., a map of conilpotent cocommutative coalgebras $f: \cliels(\fg) \to \cliels(\fh)$).
This map determines functorially a map of $E_n$ algebras
\[
\UU_n f: \UU_n \fg \to \UU_n \fh
\]
between their enveloping $E_n$ algebras.
The centralizer of this map ${\frak Z}_{E_n}(\UU_n f)$ is an $E_n$-algebra modeled by the factorization algebra 
\[
\clies(\Omega^* \otimes \fg, \cliels(\Omega^*_c \otimes \fh)_f)
\]
equipped with a convolution-type product,
where the subscript $f$ indicates how $\cliels(\Omega^*_c \otimes \fh)$ is a module over $\Omega^* \otimes \fg$.
\end{thm}

@@

Our proof involves explicit manipulations with cochain complexes and the poset of opens in~$\RR^n$.
To connect that setting with the abstract $\infty$-categorical setting above,
we leverage deep, prior work:
\begin{itemize}
\item Lurie \cite{LurieHA} explains why the $\infty$-category of $E_n$ algebras is equivalent to the homotopy-coherent version of locally constant prefactorization algebras on $\RR^n$.  
In fact, he simplifies the situation a bit more. 
Let $\Disk_n^\sqcup$ denote the colored operad whose colors are balls in $\RR^n$ and whose spaces of operations are either empty or a point, depending on whether the input balls are pairwise disjoint and subsets of the output ball. 
One can work with locally constant, homotopy-coherent $\Disk_n^\sqcup$-algebras.
\item Knudsen verifies that we can model the enveloping $E_n$ algebra by the factorization algebra $\bU_n \fg$ described earlier.
\item Lurie and Francis give a characterization of the centralizer ${\frak Z}_{E_n}(f)$ of any $E_n$ algebra map $\phi: A \to B$ as the ``internal hom'' in left $\int_{S^{n-1}}A$-modules from $A$ to $B_\phi$, where $B_\phi$ denotes $B$ viewed as a left module via the map~$\phi$.
\item In combination, the centralizer is characterized up to quasi-isomorphism, 
since it is easy to compute the factorization homology of the enveloping algebra $\UU_n \fg$ over a sphere.
\end{itemize}
In \S2 we review these results in more detail with an emphasis on what we need for our central theorem.

Here is an outline of our proof:
\begin{enumerate}
\item Let ${\bf f}: \cliels(\Omega_c^* \otimes \fg) \to \cliels(\Omega_c^* \otimes \fh)$ denote a map of factorization algebras that models with map $\UU_n f$ between enveloping algebras. 
We use it to produce an explicit factorization algebra $\clies(\Omega \otimes \fg, \cliels(\Omega_c^* \otimes \fh)_f)$ as a kind of ``convolution factorization algebra.'' 
\item We show this object fits canonically into a centralizer diagram: there is a map of factorization algebras
\[
\clies(\Omega \otimes \fg, \cliels(\Omega_c^* \otimes \fh)_f) \otimes \bU_n \fg \to \cliels(\Omega_c^* \otimes \fh)
\]
such that precomposing with the map $1 \otimes \id_{\UU_n \fg}$ is the map~${\bf f}$.
Fitting into such a diagram guarantees a canonical map 
\[
\clies(\Omega \otimes \fg, \cliels(\Omega_c^* \otimes \fh)_f) \to \bZ({\bf f})
\]
as factorization algebras. 
\item We then verify that this map is a quasi-isomorphism on disks, by the Lurie-Francis result mentioned above. 
\end{enumerate}
Hence it induces a weak equivalence of the associated factorization algebras and hence as $E_n$ algebras.

@@

\begin{cor}
\label{thm: center}
The center of the enveloping $E_n$ algebra $\UU_n\fg$ is the $E_n$ algebra $\clies(\fg, \UU_n\fg)$. 
When $k$ is $\RR$ or $\CC$, the 
center is modeled by the locally constant factorization algebra that assigns
\[
\clies(\fg \otimes \Omega^*(U), \cliels( \fg \otimes \Omega^*_c(U)))
\]
to each open set $U \subset \RR^n$.
\end{cor}

@@

Having an explicit presentation for the centralizer of a map of $E_n$ algebras leads to a calculation of factorization homology.
The enveloping $E_n$ algebra is the homotopy $O(n)$-fixed points, or a $\mathrm{Disk}_n$-algebra in the sense of~\cite{AF},
and hence determines a factorization algebra on any un-oriented $n$-dimensional manifold \cite{Knudsen}.
Therefore, for a closed $n$-dimensional manifold $M$, one has
\[
\int_M {\frak Z}_{E_n}(\UU_n \rho) \simeq \clies(\fg \otimes \Omega^*(M), \cliels( \fh \otimes \Omega^*(M))).
\]
Since $\Omega^*(S^n) \simeq \CC[\epsilon_n]$, where $\epsilon_n$ is a formal variable with $|\epsilon_n| = n$ and $\epsilon_n^2 = 0$, we have
\[
\int_{S^n} {\frak Z}_{E_n}(\UU_n \rho) \simeq \clies(\fg[\epsilon_n], \cliels( \fh[\epsilon_n]))
\]
For $n=1$, this recovers a theorem of Tamarkin and Tsygan \cite{TT} on the Hochschild cohomology of differential operators on a Lie group $G$;
see Example~\ref{eg: TT}.

@@

\section{Background}

@@

\begin{dfn}\label{D:centralizer}
For a map $f: A \to B$ of $E_n$ algebras in $\cC$, 
the {\em centralizer} ${\frak Z}_{E_n}(f)$ is the $E_n$ algebra in $\cC$ that is universal among those that fit in a commuting diagram
\[
\begin{tikzcd}
& {\frak Z}_{E_n}(f) \otimes A \arrow[dr] & \\
A \arrow[ur, "u \otimes \id"] \arrow[rr, "f"] && B
\end{tikzcd}
\]
where the arrow in the upper left is the tensor product of the unit map $u: 1_\cC \to {\frak Z}_{E_n}(f)$ and the identity map $\id: A \to A$.
The {\em center} of an $E_n$ algebra $A$ is the centralizer of its identity morphism $\id_A: A \to A$. 
We  denote it ${\frak Z}_{E_n}(A) := {\frak Z}_{E_n}(\id_A)$.
\end{dfn}

@@

\begin{prp}
\label{T:centralizer=inthom} 
The centralizer ${\frak Z}_{E_n}(f)$ exists and can be identified with the classifying object for maps from $A$ to $B$ in the $\infty$-category $\Mod^{E_n}_A(\cC)$. \mahmoud{we should probably spell out the meaning of the classifying object in this case to make it obvious that the centralizer is the classifying object}
\end{prp}

@@

\begin{prp}
\label{P:ModentoModSn}
Let $\cC^\otimes$ be a presentable symmetric monoidal stable $\infty$-category whose tensor product preserves colimits in each variable separately.
For $A$ be an $E_n$ algebra in $\cC$,
the $\infty$-category $\Mod^{E_n}_A(\cC)$ is equivalent to the $\infty$-category $\LMod_{\int_{S^{n-1} A}}(\cC)$.
\end{prp}

@@

Recall the overall strategy.
First, we define a factorization algebra $\clies(\Omega^* \otimes \fg, (\bU_n \fh)_f)$ as a kind of convolution factorization algebra.
Then we get to the heart of the construction:
we show that this convolution algebra naturally sits inside a centralizer diagram.
By the universal property of the centralizer, we then obtain 
a canonical map 
\[
\theta_{{\bf f}}: \clies\big(\fg\otimes \Omega , B \big) \longrightarrow  \bZ(\mathbf{f})
\]
where $\bZ(\mathbf{f})$ is some locally constant factorization algebra that models the centralizer ${\frak Z}(f)$ of the map $f$.
It is then a direct computation to verify $\theta_f$ is a quasi-isomorphism,
using the Francis-Lurie result mentioned earlier.

@@

\subsection{Standard manipulations with $L_\infty$ algebras and their modules}

@@

First, recall that an $L_\infty$ algebra $\fg$, with its collection of brackets $\{\ell_n\}_{n \geq 1}$ is fully encoded by its dg conilpotent cocommutative coalgebra
\[
\cliels(\fg) = \bigg(\Sym(\fg[1]) \; , \; \d = \sum_{n \geq 1} \ell_n\bigg)
\]
where the sum of the brackets provides a square-zero coderivation.
The square-zero condition efficiently encodes the higher Jacobi relations.
This coalgebra is canonically coaugmented by the inclusion of the base field $k \xto{\simeq} \Sym^0(\fg[1])$.
Let $\overline{\cliels(\fg)} \subset \cliels(\fg)$ denote the subcoalgebra given by the direct sum over positive symmetric powers of $\fg[1]$,
which can be identified with both the kernel of the counit map as well as cokernel of the coaugmentation map.

@@

This complex $\clies(\fg,\cliels(\fh)_f)$ encodes the deformation theory for $L_\infty$ maps around the map $f$.
That is, in a sufficiently sophisticated geometric setting, it is the tangent complex to the mapping space of $L_\infty$ maps from $\fg$ to~$\fh$.
One should view $f$ as the basepoint for this tangent complex.
Due to the splitting
\[
\cliels(\fg) = k \oplus \overline{\cliels(\fg)},
\]
we have a decomposition
\[
\clies(\fg,\cliels(\fh)_f) \cong \cliels(\fh) \oplus \Hom^\bullet(\overline{\cliels(\fg)}, \cliels(\fh)_f),
\]
which plays a crucial role in our argument.

Indeed, consider the canonical evaluation pairing
\[
\ev_{f}: \clies(\fg,\cliels(\fh)_f) \otimes \cliels(\fg) \to \cliels(\fh)
\]
sending $(1 + g, x)$ to $f(x) + g(x)$, where $g \in \Hom^\bullet(\overline{\cliels(\fg)}, \cliels(\fh)_f)$.
In this sense, we see how the Lie algebra cochains arising from $f$ encodes deformations.

\subsection{Defining the convolution factorization algebra}

@@

\begin{proof}
Recall from Section~\ref{sec: centralizer} that 
\begin{align*}
{\frak Z}_{E_n}(f) &\simeq {{\rm Mor}}_{\Mod^{E_n}_{\UU_n\fg}}(\UU_n \fg, (\UU_n \fh)_f) \\
&\simeq {\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n\fg}}(\UU_n \fg, (\UU_n \fh)_f)
\end{align*}
where 
\begin{itemize}
\item[-] $(\UU_n \fh)_f$ denotes the object in $\Mod^{E_n}_{\UU_n\fg}$ --- equivalently, in $\LMod_{\int_{S^{n-1}}\UU_n}$ --- determined by~$f$, 
\item[-] ${\rm Mor}_{\Mod^{E_n}_{\UU_n\fg}}(\UU_n \fg, (\UU_n \fh)_f)$ denotes the classifying object for maps (i.e. an internal mapping object) from $\UU_n\fg$ to $(\UU_n \fh)_f$ in the $\infty$-category $\Mod^{E_n}_{\UU_n\fg}$, and
\item[-] ${\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n\fg}} (\UU_n \fg, (\UU_n \fh)_f)$ denotes the classifying object for maps from ${\UU_n\fg}$ to $\UU_n \fh$ in the $\infty$-category $\LMod_{\int_{S^{n-1}}\UU_n\fg}$. 
\end{itemize}
Note that $\int_{S^{n-1}}\UU_n\fg$ is an $E_1$ algebra equivalent to the dg algebra $U(\fg \otimes k[\epsilon_{n-1}])$.
This identification holds because the rational $(n-1)$-sphere is formal, and hence its cochains are quasi-isomorphic to its cohomology $k[\epsilon_{n-1}]$.

Using the canonical inclusion $i: U\fg \to U(\fg \otimes k[\epsilon_{n-1}])$,
we find
\[
k \otimes_{U\fg} U(\fg \otimes k[\epsilon_{n-1}]) \simeq \Sym(\fg[1-n]).
\]
Recall from Section~\ref{sec: enveloping} that $\UU_n \fg$ admits two convenient models:
as a factorization algebra by $\bU_n \fg$ and as a strict algebra over a colored operad $\Disk_n$ assigning $\Sym(\fg[1-n])$ to each disk.
Base change thus gives rise to an equivalence 
\[
{\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n}} (\UU_n \fg, (\UU_n \fh)_f)  \simeq {\rm Mor}_{U\fg} (k, (\UU_n \fh)_f)
\]
of underlying cochain complexes, i.e. an equivalence after applying the forgetful functor. 
The right hand side is modeled by Lie algebra cochains of $\fg$ with coefficients in~$(\UU_n \fh)_f$, as desired.
Hence the map $\theta_{\bf f}$ is a quasi-isomorphism on any disk, as needed.
\end{proof}

@@

The universal property of centralizer (recall definition~\ref{D:centralizer}) implies that 
for any maps $A\stackrel{f}\to B$ and $B\stackrel{g}\to C$ of $E_n$-algebras, 
there is a natural morphism
\begin{equation}
\label{eqdef:canonicaltocentralizers} 
{\frak Z}_{E_n}(g) \otimes {\frak Z}_{E_n}(f) \longrightarrow {\frak Z}_{E_n}(g\circ f)
\end{equation}
in the $\infty$-category of $E_n$-algebras that arises from  
following commutative diagram of $E_n$-algebras:
\[
\begin{tikzcd}
&   {\frak Z}_{E_n}(g) \otimes  {\frak Z}_{E_n}(f) \otimes A \arrow[rr, "\id\otimes \ev_f"] &&  {\frak Z}_{E_n}(g) \otimes  B \arrow[dr, "\ev_g"]\\
A \arrow[ur, "1\otimes \id_A"] \arrow[rr, "f"] && B \arrow[rr, "g"] \arrow[ur, "1\otimes \id_B"] && C. 
\end{tikzcd}
\]
When $f=g=\id_A:A\to A$, we thus obtain a canonical morphism 
\begin{equation} 
\label{eq:dgAssofcenter}
{\frak Z}_{E_n}(A){\otimes} {\frak Z}_{E_n}(A) \longrightarrow {\frak Z}_{E_n}(A).
\end{equation}
Lurie \cite{HA} has proved that this multiplication makes the center into an $E_1$ algebra in $E_n$-algebras 
and therefore an $E_{n+1}$-algebra, by Dunn additivity. 
%To be precise, there is the following result.
%
%\begin{prp}[\cite{LurieHA} Section 5] 
%\label{P:PtyCenter}
%\begin{itemize}
% \item The canonical map~\eqref{eq:dgAssofcenter} makes the center ${\frak Z}_{E_n}(A)$ into an $E_1$-algebra in the symmetric monoidal category of 
% $E_n$-algebras.
% \item There is a canonical equivalence of the $\infty$-category $E_1\mathrm{-Alg}(E_n\mathrm{-Alg})$ with $E_{n+1}\mathrm{-Alg}$.
%\end{itemize}
%\end{prp}

A compelling aspect of our construction is that it lets one see these properties in a barehanded fashion,
using familiar formulas with $L_\infty$ algebras.
(More accurately, via composition of convolution algebras.)
The goal of this section is to prove directly the following result.

\owen{I'm pooping out, but it should be straightforward to revise this in light of our revisions above.}

>>>>

Many notions from ordinary algebra admit natural generalizations to $E_n$ algebras.
For instance, to each Lie algebra $\fg$ (and more generally $L_\infty$ algebra),
there is an {\em enveloping $E_n$ algebra} $\UU_n \fg$, thanks to \cite{Knudsen}.
Similarly, every $E_n$ algebra $A$ has a {\em center} ${\frak Z}_n(A)$, which is an $E_{n+1}$ algebra and hence more commutative than~$A$.
More generally, for any map of $E_n$ algebras $f: A \to B$, there is a {\em centralizer} ${\frak Z}_n(f)$, 
which is a generalization of the commutant.
We review these notions more fully in Section~\ref{sec: background}.

Our work here relies on a concrete and convenient model for these enveloping $E_n$ algebras by factorization algebras.
In particular, thanks again to \cite{Knudsen}, 
we know that the $E_n$ enveloping algebra $\UU_n \fg$ admits a model $\bU_n \fg$ whose underlying functor on the poset of open sets in $\RR^n$ assigns $\cliels(\Omega_c^*(V) \otimes \fg)$ to each open set~$V$.
There is another factorization algebra whose underlying assigns $\clies(\Omega^*(V) \otimes \fg)$ to each open~$V$.
Our paper shows that such factorization algebras model other important $E_n$ algebras, notably centralizers.

\begin{thm}
\label{thm: centralizer}
Let $\fg$ and $\fh$ be $L_\infty$ algebras over the real or complex numbers, 
and let $f: \fg \rightsquigarrow \fh$ be a homotopy-coherent morphism of $L_\infty$ algebras
(i.e., a map of conilpotent cocommutative coalgebras $f: \cliels(\fg) \to \cliels(\fh)$).
This map determines functorially a map of $E_n$ algebras
\[
\UU_n f: \UU_n \fg \to \UU_n \fh
\]
between their enveloping $E_n$ algebras.
The centralizer of this map ${\frak Z}_n(\UU_n f)$ is an $E_n$-algebra modeled by the factorization algebra 
\[
\clies(\Omega^* \otimes \fg, \cliels(\Omega^*_c \otimes \fh)_f)
\]
equipped with a convolution-type product,
where the subscript $f$ indicates how $\cliels(\Omega^*_c \otimes \fh)$ is a module over $\Omega^* \otimes \fg$.
\end{thm}

@@

Our proof involves explicit manipulations with cochain complexes and the poset of opens in~$\RR^n$.
To connect that setting with the abstract $\infty$-categorical setting above,
we leverage deep, prior work:
\begin{itemize}
\item Lurie \cite{LurieHA} explains why the $\infty$-category of $E_n$ algebras is equivalent to the homotopy-coherent version of locally constant prefactorization algebras on $\RR^n$.  
In fact, he simplifies the situation a bit more. 
Let $\Disk_n^\sqcup$ denote the colored operad whose colors are balls in $\RR^n$ and whose spaces of operations are either empty or a point, depending on whether the input balls are pairwise disjoint and subsets of the output ball. 
One can work with locally constant, homotopy-coherent $\Disk_n^\sqcup$-algebras.
\item Knudsen verifies that we can model the enveloping $E_n$ algebra by the factorization algebra $\bU_n \fg$ described earlier.
\item Francis and Lurie give a characterization of the centralizer ${\frak Z}_n(f)$ of any $E_n$ algebra map $\phi: A \to B$ as the ``internal hom'' in left $\int_{S^{n-1}}A$-modules from $A$ to $B_\phi$, where $B_\phi$ denotes $B$ viewed as a left module via the map~$\phi$.
\item In combination, the centralizer is characterized up to quasi-isomorphism, 
since it is easy to compute the factorization homology of the enveloping algebra $\UU_n \fg$ over a sphere.
\end{itemize}
In \S2 we review these results in more detail with an emphasis on what we need for our central theorem.

Here is an outline of our proof:
\begin{enumerate}
\item Let ${\bf f}: \cliels(\Omega_c^* \otimes \fg) \to \cliels(\Omega_c^* \otimes \fh)$ denote a map of factorization algebras that models with map $\UU_n f$ between enveloping algebras. 
We use it to produce an explicit factorization algebra $\clies(\Omega \otimes \fg, \cliels(\Omega_c^* \otimes \fh)_f)$ as a kind of ``convolution factorization algebra.'' 
\item We show this object fits canonically into a centralizer diagram: there is a map of factorization algebras
\[
\clies(\Omega \otimes \fg, \cliels(\Omega_c^* \otimes \fh)_f) \otimes \bU_n \fg \to \cliels(\Omega_c^* \otimes \fh)
\]
such that precomposing with the map $1 \otimes \id_{\UU_n \fg}$ is the map~${\bf f}$.
Fitting into such a diagram guarantees a canonical map 
\[
\clies(\Omega \otimes \fg, \cliels(\Omega_c^* \otimes \fh)_f) \to \bZ_n({\bf f})
\]
as factorization algebras, where $\bZ({\bf f})$ is some factorization algebra modeling the centralizer~${\frak Z}_n(f)$. 
\item We then verify that this map is a quasi-isomorphism on disks, by the Francis-Lurie result mentioned above. 
\end{enumerate}
Hence it induces a weak equivalence of the associated factorization algebras and hence as $E_n$ algebras.

@@

\begin{cor}
\label{thm: center}
The center ${\frak Z}_n(\fg)$ of the enveloping $E_n$ algebra $\UU_n\fg$ is the $E_n$ algebra $\clies(\fg, \UU_n\fg)$. 
When $k$ is $\RR$ or $\CC$, the 
center is modeled by the locally constant factorization algebra that assigns
\[
\clies(\fg \otimes \Omega^*(U), \cliels( \fg \otimes \Omega^*_c(U)))
\]
to each open set $U \subset \RR^n$.
\end{cor}

@@

Having an explicit presentation for the centralizer of a map of $E_n$ algebras leads to a calculation of factorization homology.
The enveloping $E_n$ algebra is the homotopy $O(n)$-fixed points, or a $\mathrm{Disk}_n$-algebra in the sense of~\cite{AF},
and hence determines a factorization algebra on any un-oriented $n$-dimensional manifold \cite{Knudsen}.
Therefore, for a closed $n$-dimensional manifold $M$, one has
\[
\int_M {\frak Z}_n(\UU_n \rho) \simeq \clies(\fg \otimes \Omega^*(M), \cliels( \fh \otimes \Omega^*(M))).
\]
Since $\Omega^*(S^n) \simeq \CC[\epsilon_n]$, where $\epsilon_n$ is a formal variable with $|\epsilon_n| = n$ and $\epsilon_n^2 = 0$, we have
\[
\int_{S^n} {\frak Z}_n(\UU_n \rho) \simeq \clies(\fg[\epsilon_n], \cliels( \fh[\epsilon_n]))
\]
For $n=1$, this recovers a theorem of Tamarkin and Tsygan \cite{TT} on the Hochschild cohomology of differential operators on a Lie group $G$;
see Example~\ref{eg: TT}.

@@

\section{Background}
\label{sec: background}

@@

\begin{dfn}\label{D:centralizer}
For a map $f: A \to B$ of $E_n$ algebras in $\cC$, 
the {\em centralizer} ${\frak Z}_n(f)$ is the $E_n$ algebra in $\cC$ that is universal among those that fit in a commuting diagram
\[
\begin{tikzcd}
& {\frak Z}_n(f) \otimes A \arrow[dr] & \\
A \arrow[ur, "u \otimes \id"] \arrow[rr, "f"] && B
\end{tikzcd}
\]
where the arrow in the upper left is the tensor product of the unit map $u: 1_\cC \to {\frak Z}_n(f)$ and the identity map $\id: A \to A$.
The {\em center} of an $E_n$ algebra $A$ is the centralizer of its identity morphism $\id_A: A \to A$. 
We  denote it ${\frak Z}_n(A) := {\frak Z}_n(\id_A)$.
\end{dfn}

@@

\begin{prp}
\label{T:centralizer=inthom} 
The centralizer ${\frak Z}_n(f)$ exists and can be identified with the classifying object for maps from $A$ to $B$ in the $\infty$-category $\Mod^{E_n}_A(\cC)$. \mahmoud{we should probably spell out the meaning of the classifying object in this case to make it obvious that the centralizer is the classifying object}
\end{prp}

@@

\begin{prp}
\label{P:ModentoModSn}
Let $\cC^\otimes$ be a presentable symmetric monoidal stable $\infty$-category whose tensor product preserves colimits in each variable separately.
For $A$ be an $E_n$ algebra in $\cC$,
the $\infty$-category $\Mod^{E_n}_A(\cC)$ is equivalent to the $\infty$-category $\LMod_{{\int_{S^{n-1}} A}}(\cC)$.
\end{prp}

@@

Recall the overall strategy.
First, we define a factorization algebra $\clies(\Omega^* \otimes \fg, (\bU_n \fh)_f)$ as a kind of convolution factorization algebra.
Then we get to the heart of the construction:
we show that this convolution algebra naturally sits inside a centralizer diagram.
By the universal property of the centralizer, we then obtain 
a canonical map 
\[
\theta_{{\bf f}}: \clies\big(\fg\otimes \Omega , B \big) \longrightarrow  \bZ(\mathbf{f})
\]
where $\bZ_n(\mathbf{f})$ is some locally constant factorization algebra that models the centralizer ${\frak Z}_n(f)$ of the map~$f$.
It is then a direct computation to verify $\theta_f$ is a quasi-isomorphism,
using the Francis-Lurie result mentioned earlier.

@@

\subsection{Standard manipulations with $L_\infty$ algebras and their modules}
\label{sec: review of linfty}

@@

First, recall that an $L_\infty$ algebra $\fg$, with its collection of brackets $\{\ell_n\}_{n \geq 1}$ is fully encoded by its dg conilpotent cocommutative coalgebra
\[
\cliels(\fg) = \bigg(\Sym(\fg[1]) \; , \; \d = \sum_{n \geq 1} \ell_n\bigg)
\]
where the sum of the brackets provides a square-zero coderivation.
The square-zero condition efficiently encodes the higher Jacobi relations.
This coalgebra is canonically coaugmented by the inclusion of the base field $k \xto{\simeq} \Sym^0(\fg[1])$.
There is thus a subcoalgebra $\overline{\cliels(\fg)} \subset \cliels(\fg)$ given by the direct sum over positive symmetric powers of $\fg[1]$,
which can be identified with both the kernel of the counit map as well as cokernel of the coaugmentation map.
In short,
\[
\cliels(\fg) = k \oplus \overline{\cliels(\fg)}
\]
as complexes.

@@

This complex $\clies(\fg,\cliels(\fh)_f)$ encodes the deformation theory for $L_\infty$ maps around the map $f$.
That is, in a sufficiently sophisticated geometric setting, it is the tangent complex to the mapping space of $L_\infty$ maps from $\fg$ to~$\fh$.
One should view $f$ as the basepoint for this tangent complex.
Due to the splitting $\cliels(\fg) = k \oplus \overline{\cliels(\fg)}$,
we have a decomposition
\begin{align*}
\clies(\fg,\cliels(\fh)_f) 
&\cong \cliels(\fh) \oplus \Hom^\bullet(\overline{\cliels(\fg)}, \cliels(\fh)_f)\\
&\cong k \oplus \overline{\cliels(\fh)} \oplus \Hom^\bullet(\overline{\cliels(\fg)}, \cliels(\fh)_f)
\end{align*}
which plays a crucial role in our argument.

Indeed, consider the canonical evaluation pairing
\[
\ev_{f}: \clies(\fg,\cliels(\fh)_f) \otimes \cliels(\fg) \to \cliels(\fh)
\]
sending $(1 + g, x)$ to $f(x) + g(x)$, where $g \in \Hom^\bullet(\overline{\cliels(\fg)}, \cliels(\fh)_f)$.
In this sense, we see how $\clies(\fg,\cliels(\fh)_f)$ encodes deformations of~$f$.

\subsection{Defining the convolution factorization algebra}
\label{sec: dfn of centralizer fact alg}

@@

\begin{proof}
Recall from Section~\ref{sec: centralizer} that 
\begin{align*}
{\frak Z}_n(f) &\simeq {{\rm Mor}}_{\Mod^{E_n}_{\UU_n\fg}}(\UU_n \fg, (\UU_n \fh)_f) \\
&\simeq {\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n\fg}}(\UU_n \fg, (\UU_n \fh)_f)
\end{align*}
where 
\begin{itemize}
\item $(\UU_n \fh)_f$ denotes the object in $\Mod^{E_n}_{\UU_n\fg}$ --- equivalently, in $\LMod_{\int_{S^{n-1}}\UU_n}$ --- determined by~$f$, 
\item ${\rm Mor}_{\Mod^{E_n}_{\UU_n\fg}}(\UU_n \fg, (\UU_n \fh)_f)$ denotes the classifying object for maps (i.e. an internal mapping object) from $\UU_n\fg$ to $(\UU_n \fh)_f$ in the $\infty$-category $\Mod^{E_n}_{\UU_n\fg}$, and
\item ${\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n\fg}} (\UU_n \fg, (\UU_n \fh)_f)$ denotes the classifying object for maps from ${\UU_n\fg}$ to $\UU_n \fh$ in the $\infty$-category $\LMod_{\int_{S^{n-1}}\UU_n\fg}$. 
\end{itemize}
In the case at hand, this object is eminently computable.

The notation $\int_{S^{n-1}}\UU_n\fg$ produces a factorization algebra on $\RR$.
Indeed,
\begin{align*}
\int_{S^{n-1}}\UU_n\fg 
&\simeq \cliels(\Omega^*_c(\RR_{> 0} \times S^{n-1}) \otimes \fg)\\
&\simeq \cliels(\Omega^*_c(\RR_{> 0}) \otimes H^*(S^{n-1}) \otimes \fg)
\end{align*}
because $(n-1)$-sphere is formal over the rationals (or reals). 
We thus see that 
\[
\int_{S^{n-1}}\UU_n\fg \simeq \UU_1 (H^*(S^{n-1}) \otimes \fg)
\]
The cohomology of the $(n-1)$-sphere is 
\[
R_n = k[\epsilon_{n-1}]/(\epsilon_{n-1}^2),
\] 
where $|\epsilon_{n-1}| = n-1$.
Since $\UU_1 (H^*(S^{n-1}) \otimes \fg)$ is manifestly equivalent to the dg algebra~$U(\fg \otimes R_n)$,
we find that 
\[
\int_{S^{n-1}}\UU_n\fg \simeq U(\fg \otimes R_n)
\]
as $E_1$ algebras.

Recall from Section~\ref{sec: enveloping} that $\UU_n \fg$ admits two convenient models:
as a factorization algebra by $\bU_n \fg$ and as a strict algebra over a colored operad $\Disk_n$ assigning $\Sym(\fg[1-n])$ to each disk.
For $n > 1$ that is a commutative algebra.
\owen{Should I say that??? And should we remark that the $n=1$ case is known???}

We have thus reduced the situation to familiar dg algebra via the equivalence
\[
{\rm Mor}_{\LMod_{\int_{S^{n-1}} \UU_n\fg}}(\UU_n \fg, (\UU_n \fh)_f) 
\simeq 
{\rm Mor}_{\LMod_{U(\fg \otimes R_n)}} (\Sym(\fg[1-n]), (\Sym(\fh[1-n]))_f).
\]
By the inclusion of the unit $k \hookrightarrow R_n = k \oplus k[1-n]$,
we obtain a canonical inclusion $i: U\fg \to U(\fg \otimes R_n)$ of dg associative algebras,
and so
\[
k \otimes_{U\fg} U(\fg \otimes R_n) \simeq \Sym(\fg[1-n]).
\]
Base change along $i$ thus gives rise to an equivalence 
\[
{\rm Mor}_{\LMod_{U\fg}} (k, (\Sym(\fh[1-n]))_f) \simeq {\rm Mor}_{\LMod_{U(\fg \otimes R_n)}} (\Sym(\fg[1-n]), (\Sym(\fh[1-n]))_f)
\]
of underlying cochain complexes, i.e. an equivalence after applying the forgetful functor. 
The left hand side is modeled by $\clies(\fg,(\Sym(\fh[1-n]))_f)$, 
the Lie algebra cochains of $\fg$ with coefficients in~$(\UU_n \fh)_f$, as desired.
Hence the map $\theta_{\bf f}$ is a quasi-isomorphism on any disk, as needed.
\end{proof}

@@

The universal property of centralizer (recall definition~\ref{D:centralizer}) implies that 
for any maps $A\stackrel{f}\to B$ and $B\stackrel{g}\to C$ of $E_n$-algebras, 
there is a natural map of $E_n$-algebras
\begin{equation}
\label{eqdef:canonicaltocentralizers} 
{\frak Z}_n(g) \otimes {\frak Z}_n(f) \longrightarrow {\frak Z}_n(g\circ f)
\end{equation}
that arises from following commutative diagram of $E_n$-algebras:
\[
\begin{tikzcd}
&   {\frak Z}_n(g) \otimes  {\frak Z}_n(f) \otimes A \arrow[rr, "\id\otimes \ev_f"] &&  {\frak Z}_n(g) \otimes  B \arrow[dr, "\ev_g"]\\
A \arrow[ur, "1\otimes \id_A"] \arrow[rr, "f"] && B \arrow[rr, "g"] \arrow[ur, "1\otimes \id_B"] && C 
\end{tikzcd}.
\]
When $f=g=\id_A:A\to A$, we thus obtain a canonical morphism 
\begin{equation} 
\label{eq:dgAssofcenter}
{\frak Z}_n(A){\otimes} {\frak Z}_n(A) \longrightarrow {\frak Z}_n(A).
\end{equation}
Lurie \cite{HA} has proved that this multiplication makes the center into an $E_1$ algebra in $E_n$-algebras 
and therefore an $E_{n+1}$-algebra, by Dunn additivity. 
%To be precise, there is the following result.
%
%\begin{prp}[\cite{LurieHA} Section 5] 
%\label{P:PtyCenter}
%\begin{itemize}
% \item The canonical map~\eqref{eq:dgAssofcenter} makes the center ${\frak Z}_n(A)$ into an $E_1$-algebra in the symmetric monoidal category of 
% $E_n$-algebras.
% \item There is a canonical equivalence of the $\infty$-category $E_1\mathrm{-Alg}(E_n\mathrm{-Alg})$ with $E_{n+1}\mathrm{-Alg}$.
%\end{itemize}
%\end{prp}

A compelling aspect of our construction is that one can see these properties in a barehanded fashion,
using familiar formulas with $L_\infty$ algebras.
(More accurately, via composition of convolution algebras.)
The goal of this section is to prove directly the following result.

\begin{thm}
\label{T:compcentralizer}
Let $f: \fg \rightsquigarrow \fh$ and $g: \fh \rightsquigarrow \fl$ be maps of  $L_\infty$-algebras,
and let $\bold{f}: \bU_n \fg \to \bU_n \fh$ and $\bold{g}: \bU_n \fh \to \bU_n \fl$ denote the induced maps of factorization algebras.
\begin{enumerate} 
\item There is a natural map of factorization algebras
\[
(-\star-) : \bZ_n(g) \otimes \bZ_n(f) \to \bZ_n(g \circ f),
\]
given by definition~\ref{def:comp}, 
that models the canonical map 
\[
{\frak Z}_n(g) \otimes {\frak Z}_n(f) \longrightarrow {\frak Z}_n(g\circ f).
\] 
\item If $f= \fg \stackrel{\id}\to \fg$, 
then the composition $(-\star-)$ makes $\bZ_n(\fg)$ into an 
augmented associative algebra {\em on the nose} in the 1-category of factorization algebras on~$\RR^n$,
and it models the center ${\frak Z}_n(\fg)$ as an $E_1$ algebra in $E_n$ algebras.
\end{enumerate}
\end{thm}

The proof follows by a steady accumulation of natural observations.
